A Review of Lossless Data Compression Algorithms

### 2020-05-06 paper.tex
final

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{xfrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{array}
\usepackage{graphicx}
\graphicspath{ {./images/} }

@@

\section{Lempel-Ziv(lz) Compression Methods}
Also known as the LZ family,it initially consisted of LZ-77 and LZ-78 which was published by Abraham Lempel and Jacob Ziv in 1977\cite{ziv1977universal} and 1978\cite{ziv1978compression}.Also known as LZ-1 and LZ-2 respectively,both are theoretically dictionary coders.These algorithms formed the basis for a lot of variations like LZW,LZSS,LZMA and also for a lot compression schemes like DEFLATE which has been discussed later in this article.
\subsection{LZ-77 Algorithm}
LZ77 algorithms achieve compression by replacing repeated occurrences of data with references to a copy of that data existing earlier within the uncompressed data stream. A match is encoded by a pair of numbers called a length-distance pair, which is like the statement "each of the next length characters is equal to the characters exactly distance characters behind it in the uncompressed stream".

@@

\textbf{Pseudocode}

\textbf{while} input not empty \textbf{do}

prefix : longest prefix of input that begins in window

\textbf{if} prefix exists \textbf{then}

j : distance to start of prefix

k : length of prefix

a : char following prefix in input

\textbf{else
}
j := 0

k := 0

a := first char of input

\textbf{end if}

\textbf{output} (j,k,a)

s := pop k + 1 chars from front of input

discard k + 1 chars from front of window

append s to back of window

\textbf{repeat}
\subsection{LZ-78 Algorithm}
The LZ78 is also a dictionary-based compression algorithm that maintains a dictionary. The encoded output
consists of two elements: an index pertaining to the longest matching lexical entry and therefore the first non-matching
symbol. The algorithm also adds the index and symbol pair to the dictionary. When the symbol is not yet found in
the dictionary, the codeword has the index value 0 and it's added to the dictionary as well . With this method, the
algorithm constructs the dictionary.
LZ78 algorithm has the power to capture patterns and hold them indefinitely but it also features a serious drawback.
The dictionary keeps growing forever without bound. There are a lot of methods to limit dictionary size. the
easiest one is to stop adding entries and continue like a static dictionary coder or to throw the dictionary away and
start from scratch after a certain number of entries has been reached\cite{zeeh2003lempel}

\textbf{Pseudocode}

q : NIL;

\textbf{While} (there is input) \textbf{do}{

	J : next symbol from input;

	\textbf{If} (qJ exists in the dictionary) \textbf{then} {

		q : qJ;

	}

	\textbf{Else} {

		\textbf{Output} (index(q), J);

		Add qJ to the dictionary;

		q : NIL;

	}\textbf{end if}

}\textbf{repeat}

@@

Arithmetic coding is a data compression technique that encodes data (the data string) by creating a code string which represents a fractional value on the number line between 0 and 1. The coding algorithm is symbolwise recursive; i.e., it operates upon and encodes (decodes) one data symbol per iteration or recursion. On each recursion, the algorithm successively partitions an interval of the number line between 0 and 1, and retains one of the partitions as the new interval. Thus, the algorithm successively deals with smaller intervals, and the code string, viewed as a magnitude, lies in each of the nested intervals. The data string is recovered by using magnitude comparisons on the code string to recreate how the encoder must have successively partitioned and retained each nested subinterval. Arithmetic coding differs considerably from the more familiar compression coding techniques, such as prefix (Huffman) codes. Also, it should not be confused with error control coding, whose object is to detect and correct errors in computer operations.

@@

DEFLATE is a lossless data compression file format that uses a combination of LZSS and Huffman coding. It was designed by Phil Katz, for version 2 of his PKZIP archiving tool. Deflate was later specified in RFC 1951 (1996). Katz also designed the original algorithm used to construct Deflate streams. This algorithm was patented as U.S. Patent 5,051,745, and assigned to PKWARE, Inc.[2][3] As stated in the RFC document, an algorithm producing Deflate files was widely thought to be implementable in a manner not covered by patents.[1] This led to its widespread use, for example in gzip compressed files and PNG image files, in addition to the ZIP file format for which Katz originally designed it.

\vspace{0.3in}

@@

@@

This paper reports a rather different viewpoint on the whole compression domain. The energy required to send a bit via wireless transmission is close to 1000 times higher than the energy required for a regular 32 bit operation on a computer. The article reports the fact that compressing and decompressing information before and after transmission is more energy expensive compared to the case without any compression. The paper suggests solutions to this problem and they are able to achive an energy reduction of close to 51\%.

\subsection{Methodologies and Summary}
The tests were done on a Compaq Personal Server codenamed "Skiff".

The energy required for compression and decompression are almost directly proportional to time required for executing. The energy required is observed to be more for aggressively compressed data due to the large number of memory references. Even though the energy requirement is proportional to the execution time, using the fastest algorithm for compression and decompression doesn't reduce the energy footprint. They were able to conclude the fact that reducing energy is not as simple as picking the fastest compression algorithm.

@@

@@

Some of the other interesting papers we found are cited below.

\textbf{Towards Analysis-friendly Face Representation with Scalable Feature and Texture Compression \cite{wang2020towards}}

\textbf{On the Compressive Power of Boolean Threshold Autoencoders \cite{melkman2020compressive}}

@@

@@

\textbf{Review References}

\begin{enumerate}
	\setcounter{enumi}{17}

	\item D. Benedetto, E. Caglioti, and V. Loreto. Language
	trees and zipping. Physical Review Letters, 88(4), 28
	Jan. 2002.

	\item A. Bratko, G. V. Cormack, B. Filipi˘c, T. R. Lynam,
	and B. Zupan. Spam filtering using statistical data
	compression models. Journal of Machine Learning
	Research, 7:2673–2698, 2006.

	\item M. Burrows and D. J. Wheeler. A block-sorting
	lossless data compression algorithm. Technical Report
	SRC-RR-124, Digiral Systems Research Center, 1994.

	\item R. Cilibrasi and P. Vit´anyi. Clustering by
	compression. IEEE Transactions on Information
	Theory, 51(4):1523–1545, 2005.

	\item J. G. Cleary and I. H. Witten. Data compression using
	adaptive coding and partial string matching. IEEE
	Transactions on Communications,
	COM-32(4):396–402, 1984.

	\item G. Cormack and R. N. S. Horspool. Data compression
	using dynamic markov modelling. The Computer
	Journal, 30(6):541–550, 1987.

	\item K. Crammer, O. Dekel, J. Keshet, S. Shalev-Shwartz,
	and Y. Singer. Online passive-agressive algorithm.
	Journal of Machine Learning Research, 7:551–585,
	2006.

	\item M. Dredze, K. Crammer, and F. Pereira.
	Confidence-weighted linear classification. In
	Proceedings of 25th International Conference on
	Machine Learning, pages 264–271, 2008.

	\item D. Irani, S. Webb, C. Pu, and K. Li. Study of
	trend-stuffing on twitter through text classification. In
	Proceedings of 7th Annual Collaboration, Electronic
	messaging, Anti-Abuse and Spam Conference, 2010.

	\item H. Kwak, C. Lee, H. Park, and S. Moon. What is
	twitter, a social network or a news media? In
	Proceedings of 19th International Conference on
	World Wide Web, pages 591–600, 2010.

	\item M. Li, X. Chen, X. Li, B. Ma, and P. M. B. Vit´anyi.
	The similarity metric. IEEE Transactions on
	Information Theory, 50(12):3250–3264, 2004.

	\item M. Li and P. Vit´anyi. An Introduction to Kolmogorov
	Complexity and Its Applications. Springer, 2nd
	edition, 1997.

	\item Y. Marton, N. Wu, and L. Hellerstein. On
	compression-based text classification. In Proceedings of
	the 27th European Conference on Information
	Retrieval, pages 300–314, 2005.

	\item T. Sakaki, M. Okazaki, and Y. Matsuo. Earthquake
	shakes twitter users: Real-time event detection by
	social sensors. In Proceedings of 19th International
	Conference on World Wide Web, pages 851–860, 2010.

	\item B. Sriram, D. Fuhry, and M. Demirbas. Short text
	classification in twitter to improve information
	filtering. In Proceedings of 33rd International ACM
	SIGIR Conference on Research and Development in
	Information Retrieval, pages 841–842, 2010.

	\item I. H. Witten, A. Moffat, and T. C. Bell. Managing
	Gigabytes: compressing and indexing documents and
	images. Morgan Kaufmann, 2nd edition, 1999.

	\item J. Ziv and A. Lempel. A universal algorithm for
	sequential data compression. IEEE Transactions on
	Information Theory, IT-23(3):337–343, 1977.

	\item Advanced RISC Machines Ltd (ARM). Writing Efficient
	C for ARM, Jan. 1998. Application Note 34.

	\item T. M. Austin and D. C. Burger. SimpleScalar version 4.0
	release. Tutorial in conjunction with 34th Annual International Symposium on Microarchitecture, Dec. 2001.

	\item T. Bell and D. Kulp. Longest match string searching for
	Ziv-Lempel compression. Technical Report 06/89, Department of Computer Science, University of Canterbury,
	New Zealand, 1989.

	\item T. Bell, M. Powell, J. Horlor, and R. Arnold. The Canterbury Corpus. http://www.corpus.canterbury.ac.nz/.

	\item T. Bell, I. H. Witten, and J. G. Cleary. Modeling for text
	compression. ACM Computing Surveys, 21(4):557–591,
	1989.

	\item J. Bilmes, K. Asanovic, C.-W. Chin, and J. Demmel. Op- ´
	timizing matrix multiply using PHiPAC: a portable, highperformance, ANSI C coding methodology. In 11th ACM
	International Conference on Supercomputing, July 1997.

	\item D. C. Burger and T. M. Austin. The SimpleScalar tool
	set, version 2.0. Technical Report CS-TR-97-1342, University of Wisconsin, Madison, June 1997.

	\item M. Burrows and D. J. Wheeler. A block-sorting lossless
	data compression algorithm. Technical Report 124, Digital Systems Research Center, May 1994.

	\item J. Gailly and M. Adler. zlib. http://www.gzip.org/zlib.

	\item J. Gailly, Maintainer. comp.compression Internet
	newsgroup: Frequently Asked Questions, Sept. 1999.

	\item J. Gilchrist. Archive comparison test.
	http://compression.ca.

	\item P. J. Havinga. Energy efficiency of error correction on
	wireless systems. In IEEE Wireless Communications and
	Networking Conference, Sept. 1999.

	\item J. Hicks et al. Compaq personal server
	project, 1999. http://crl.research.compaq.com
	/projects/personalserver/default.htm.

	\item B. C. Housel and D. B. Lindquist. Webexpress: a system
	for optimizing web browsing in a wireless environment.
	In Proceedings of the Second Annual International Conference on Mobile Computing and Networking, 1996.

	\item J. J. Hunt, K.-P. Vo, and W. F. Tichy. An empirical study
	of delta algorithms. In Software configuration management: ICSE 96 SCM-6 Workshop. Springer, 1996.

	\item Hyperspace Communications, Inc.
	Mod gzip. http://www.ehyperspace.com /htmlonly/products/mod gzip.html.

	\item Intel Corporation. SA-110 Microprocessor Technical Reference Manual, December 2000.

	\item Intel Corporation. Intel StrongARM SA-1110 Microprocessor Developer’s Manual, October 2001.

	\item V. Jacobson. RFC 1144: Compressing TCP/IP headers
	for low-speed serial links, Feb. 1990.

	\item K. Jamieson. Implementation of a power-saving protocol for ad hoc wireless networks. Master’s thesis, Massachusetts Institute of Technology, Feb. 2002.

	\item P. Jannesen et. al. (n)compress. available, among other
	places, in Redhat 7.2 distribution of Linux.

	\item K. Koskelin, K. Barr, and K. Asanovic. Eprof: An en- ´
	ergy profiler for the iPaq. In 2nd Annual Student Oxygen
	Workshop. MIT Project Oxygen, 2002.

	\item R. Krashinsky. Efficient web browsing for mobile clients
	using HTTP compression. Technical Report MIT-LCSTR-882, MIT Lab for Computer Science, Jan. 2003.

	\item J. Lilley, J. Yang, H. Balakrishnan, and S. Seshan. A unified header compression framework for low-bandwidth
	links. In 6th ACM MOBICOM, Aug. 2000.

	\item Lycos. Lycos 50, Sept. 2002. Top 50 searches on Lycos
	for the week ending September 21, 2002.

	\item A. Miyoshi, C. Lefurgy, E. V. Hensbergen, R. Rajamony,
	and R. Rajkumar. Critical power slope: Understanding
	the runtime effects of frequency scaling. In International
	Conference on Supercomputing, June 2002.

	\item J. C. Mogul. Trace-based analysis of duplicate suppression in HTTP. Technical Report 99.2, Compaq Computer
	Corporation, Nov. 1999.

	\item J. C. Mogul, F. Douglis, A. Feldmann, and B. Krishnamurthy. Potential benefits of delta encoding and data
	compression for HTTP. Technical Report 97/4a, Compaq Computer Corporation, Dec. 1997.

	\item J. Montanaro et al. A 160-mhz, 32-b, 0.5-w CMOS RISC
	microprocessor. IEEE Journal of Solid-State Circuits,
	31(11), Nov. 1996.

	\item N. Motgi and A. Mukherjee. Network conscious text
	compression systems (NCTCSys). In Proceedings of
	International Conference on Information and Theory:
	Coding and Computing, 2001.

	\item A. Muthitacharoen, B. Chen, and D. Mazi`eres. A lowbandwidth network file system. In Proceedings of the
	18th ACM Symposium on Operating Systems Principles (SOSP ’01), pages 174–187, Chateau Lake Louise,
	Banff, Canada, October 2001.

	\item Nielsen NetRatings Audience Measurement Service. Top
	25 U.S Properties; Week of Sept 15th., Sept. 2002.

	\item M. F. Oberhumer. LZO.
	http://www.oberhumer.com/opensource/lzo/.

	\item A. Peymandoust, T. Simuni ˘ c, and G. D. Micheli. Low ´
	power embedded software optimization using symbolic
	algebra. In Design, Automation and Test in Europe, 2002.

	\item J. Santos and D. Wetherall. Increasing effective link
	bandwidth by suppressing replicated data. In USENIX
	Annual Technical Conference, June 1998.

	\item K. Sayood. Introduction to data compression. Morgan
	Kaufman Publishers, second edition, 2002.

	\item J. Seward. bzip2. http://www.spec.org
	/osg/cpu2000/CINT2000/256.bzip2/docs/256.bzip2.html.

	\item J. Seward. e2comp bzip2 library.
	http://cvs.bofh.asn.au/e2compr/index.html.

	\item A. Shacham, B. Monsour, R. Pereira, and M. Thomas.
	RFC 3173: IP payload compression protocol, Sept. 2001.

	\item D. Shkarin. PPMd.
	ftp://ftp.elf.stuba.sk/pub/pc/pack/ppmdi1.rar.

	\item A. Sinha, A. Wang, and A. Chandrakasan. Algorithmic
	transforms for efficient energy scalable computation. In
	IEEE International Symposium on Low Power Electronics and Design, August 2000.

	\item Standard Performance Evaluation Corporation.
	CPU2000, 2000.

	\item C. N. Taylor and S. Dey. Adaptive image compression
	for wireless multimedia communication. In IEEE International Conference on Communication, June 2001.

	\item A. Tridgell. Efficient Algorithms for Sorting and Synchronization. PhD thesis, Australian National University,
	Apr. 2000.

	\item T. Simuni ˘ c, L. Benini, and G. D. Micheli. Energy- ´
	efficient design of battery-powered embedded systems.
	In IEEE International Symposium on Low Power Electronics and Design, 1999.

	\item T. Simuni ˘ c, L. Benini, G. D. Micheli, and M. Hans. ´
	Source code optimization and profiling of energy consumption in embedded systems. In International Symposium on System Synthesis, 2000.

	\item M. A. Viredaz and D. A. Wallach. Power evaluation of
	Itsy version 2.4. Technical Report TN-59, Compaq Computer Corporation, February 2001.

	\item H. Yang, G. R. Gao, A. Marquez, G. Cai, and Z. Hu.
	Power and energy impact of loop transformations. In
	Workshop on Compilers and Operating Systems for
	Low Power 2001, Parallel Architecture and Compilation
	Techniques, Sept. 2001.

	\item BEERS, A., AGRAWALA, M., AND CHADDA, N. 1996. Rendering
	from Compressed Textures. In Proceedings of ACM SIGGRAPH
	96, 373–378.

	\item BPTC, 2010. ARB texture compression bptc. Available online:
	www.opengl.org/registry/specs/ARB/texture compression bptc.txt.

	\item CAMPBELL, G., DEFANTI, T. A., FREDERIKSEN, J., JOYCE,
	S. A., LESKE, L. A., LINDBERG, J. A., AND SANDIN, D. J.
	1986. Two Bit/Pixel Full Color Encoding. In Computer Graphics (Proceedings of ACM SIGGRAPH 86), 215–223.

	\item DELP, E. J., AND MITCHELL, O. R. 1979. Image Compression
	using Block Truncation Coding. IEEE Transactions on Communications 2, 9, 1335–1342.

	\item FENNEY, S. 2003. Texture Compression using Low-Frequency
	Signal Modulation. In Graphics Hardware, ACM Press, 84–91.
	INADA, T., AND MCCOOL, M. 2006. Compressed Lossless Texture Representation and Caching. In Graphics Hardware, 111–	120.

	\item IOURCHA, K., NAYAK, K., AND HONG, Z., 1999. System and
	Method for Fixed-Rate Block-Based Image Compression with
	Inferred Pixel Values. US Patent 5,956,431.

	\item JPEG, 2000. JPEG 2—ISO/IEC 15444-1:2005. Available online:http://www.jpeg.org/jpeg2000/.

	\item KNITTEL, G., SCHILLING, A. G., KUGLER, A., AND STRASSER, W. 1996. Hardware for Superior Texture Performance. Computers and Graphics, 20, 4, 475–481.

	\item MICROSOFT, 2006. HD Photo. Available online:
	http:/www.microsoft.com/windows/windowsmedia/forpros/
	wmphoto/default.aspx.

	\item OWENS, J. D. 2005. Streaming Architectures and Technology
	Trends. In GPU Gems 2. Addison-Wesley, 457–470.

	\item RASMUSSON, J., STROM¨ , J., WENNERSTEN, P., DOGGETT,
	M., AND AKENINE-MOLLER ¨ , T. 2010. Texture Compression of Light Maps using Smooth Profile Functions. In HighPerformance Graphics, 143–152.

	\item STROM¨ , J., AND AKENINE-MOLLER ¨ , T. 2005. iPACKMAN:
	High-Quality, Low-Complexity Texture Compression for Mobile Phones. In Graphics Hardware, 63–70.
	\item STROM¨ , J., AND PETTERSSON, M. 2007. ETC2: Texture Compression using Invalid Combinations. In Graphics Hardware,
	49–54.

	\item SUEHRING ¨ , K. 2009. JM Software H.264/AVC.
	http://iphome.hhi.de/suehring/tml/.
	TORBORG, J., AND KAJIYA, J. 1996. Talisman: Commodity Realtime 3D Graphics for the PC. In Proceedings of SIGGRAPH,
	353–364.

	\item VAN WAVEREN, J., 2006. Real-Time Texture Streaming and
	Decompression. Id Software Technical Report, available at
	http://software.intel.com/file/17248/.
	\item WEINBERGER, M., SEROUSSI, G., AND SAPIRO, G. 1996.
	LOCO-I: A Low Complexity, Context-Based, Lossless Image
	Compression Algorithm. In Proc. IEEE Data Compression Conference, Snowbird, Utah, March-April 1996.

	\item WHEELER, F., 1996. Adaptive Arithmetic Coding Source Code.
	available at http://www.cipr.rpi.edu/ wheeler/ac/.

	\item WITTEN, I. H., NEAL, R. M., AND CLEARY, J. G. 1987. Arithmetic Coding for Data Compression. Communications of the	ACM 30, 6.

	\item Edwin Catmull. “Computer Display of Curved Surfaces”, Proc. IEEE Conf. Computer Graphics, Pattern Recognition, and Data Structures May 1975, 11–17.

	\item Andrew C. Beers, Maneesh Agrawala, and Navin
	Chadda. “Rendering from Compressed Textures”,
	Computer Graphics, Proc. SIGGRAPH 7(3),
	Aug.1996, 373–378

	\item James Kajiya, Ivan Sutherland, and Edward Cheadle.
	“A Random-Access Video Frame Buffer”, Proc. IEEE
	Computer Graphics, Pattern Recognition, and Data
	Structures May 1975, 1–6.

	\item Paul Heckbert. “Color Image Quantisation for Frame
	Buffer Display”, Computer Graphics 16(3), July 1982,
	297–307.

	\item Xiaolin Wu. “Color Quantization by Dynamic Programming and Principal Analysis”, ACM Transactions
	on Graphics 11(4), Oct. 1992, 348–372.

	\item Lance Williams. “Pyramidal Parametrics”, Computer
	Graphics 7(3), July 1983, 1–11.

	\item E. Delp and O. Mitchell. “Image Compression Using
	Block Truncation Coding”, IEEE Trans. on Communications. Vol.COM-2 (9), Sept. 1979, 1335–1342.

	\item Graham Campbell et al. “Two bit/pixel full color encoding”, Computer Graphics 20(4), August 1986, 215–
	223.

	\item G. Knittel, A. Schilling, A. Kugler, and W. Strasser.
	“Hardware for Superior Texture Performance”, Proceedings of the 10th Eurographics Workshop on Graphics Hardware 1995, 33–39.

	\item Konstantine Iourcha, Krishna Nayak, and Zhou Hong.
	“System and Method for Fixed-Rate Block-Based Image Compression with Inferred Pixel Values”, US
	Patent 5,956,431.

	\item L. Levkovich-Maslyuk, P. G. Kalyuzhny, and A.
	Zhirkov. “Texture Compression with Adaptive Block
	Partitions”, ACM Multimedia 2000 Nov. 2000.

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{xfrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{array}
\usepackage{graphicx}
\graphicspath{ {./images/} }
\usepackage{algorithm}
\usepackage{algorithmic}

@@

\section{Lempel-Ziv(lz) Compression Methods}
Also known as the LZ family,it initially consisted of LZ-77 and LZ-78 which was published by Abraham Lempel and Jacob Ziv in 1977\cite{ziv1977universal} and 1978\cite{ziv1978compression}.Also known as LZ-1 and LZ-2 respectively,both are theoretically dictionary coders.These algorithms formed the basis for a lot of variations like LZW,LZSS,LZMA and also for a lot compression schemes like DEFLATE which has been discussed later in this article.

\subsection{LZ-77 Algorithm}
LZ77 algorithms achieve compression by replacing repeated occurrences of data with references to a copy of that data existing earlier within the uncompressed data stream. A match is encoded by a pair of numbers called a length-distance pair, which is like the statement "each of the next length characters is equal to the characters exactly distance characters behind it in the uncompressed stream".

@@

\begin{algorithm}
	\caption{LZ-77}
	\begin{algorithmic}[0]
		\WHILE{input not empty}
		\STATE prefix : longest prefix of input that begins in window
		\IF{prefix exists}
		\STATE j : distance to start of prefix
		\STATE k : length of prefix
		\STATE a : char following prefix in input
		\IF{j := 0}
		\STATE k := 0
		\STATE a := first char of input
		\ENDIF
		\ENDIF
		\STATE \textbf{output}(j, k, a)
		\STATE s := pop k + 1 char from front of input
		\STATE discard k+1 char from front of window
		\STATE append s to back of window
		\ENDWHILE
	\end{algorithmic}
\end{algorithm}

\subsection{LZ-78 Algorithm}
The LZ78 is also a dictionary-based compression algorithm that maintains a dictionary. The encoded output
consists of two elements: an index pertaining to the longest matching lexical entry and therefore the first non-matching
symbol. The algorithm also adds the index and symbol pair to the dictionary. When the symbol is not yet found in
the dictionary, the codeword has the index value 0 and it's added to the dictionary as well . With this method, the
algorithm constructs the dictionary.
LZ78 algorithm has the power to capture patterns and hold them indefinitely but it also features a serious drawback.
The dictionary keeps growing forever without bound. There are a lot of methods to limit dictionary size. the
easiest one is to stop adding entries and continue like a static dictionary coder or to throw the dictionary away and
start from scratch after a certain number of entries has been reached\cite{zeeh2003lempel}

\begin{algorithm}
	\caption{LZ-78}
	\begin{algorithmic}[0]
		\STATE q:NIL;
		\WHILE{there is input}
		\STATE j : next symbol from input
		\IF{$q_j$ exists in the dictionary}
			\STATE q : $q_j$
		\ELSE
			\STATE \textbf{output}(index(q), j)		
			\STATE Add $q_j$ to the dictionary
			\STATE q : NIL
		\ENDIF
		\ENDWHILE

	\end{algorithmic}
\end{algorithm}

@@

Arithmetic coding \cite{witten1987arithmetic} is a data compression technique that encodes data (the data string) by creating a code string which represents a fractional value on the number line between 0 and 1. The coding algorithm is symbolwise recursive; i.e., it operates upon and encodes (decodes) one data symbol per iteration or recursion. On each recursion, the algorithm successively partitions an interval of the number line between 0 and 1, and retains one of the partitions as the new interval. Thus, the algorithm successively deals with smaller intervals, and the code string, viewed as a magnitude, lies in each of the nested intervals. The data string is recovered by using magnitude comparisons on the code string to recreate how the encoder must have successively partitioned and retained each nested subinterval. Arithmetic coding differs considerably from the more familiar compression coding techniques, such as prefix (Huffman) codes. Also, it should not be confused with error control coding, whose object is to detect and correct errors in computer operations.\cite{rissanen1979arithmetic} \cite{langdon1984introduction}

\begin{algorithm}
	\caption{Arithmetic Coding}
	\begin{algorithmic}[0]
		\STATE count source units
		\STATE interval I := \textbf{new} interval 0..1
		\STATE divide I according to rate of units
		\STATE \textbf{readSymbol}(X) \linebreak
		\WHILE{X != EOF}
		\STATE new I := subinterval I matching X
		\STATE divide I acording to rate of units
		\STATE readSymbol(X)
		\ENDWHILE
		\STATE \textbf{output}(best number from I)
	\end{algorithmic}
\end{algorithm}

For example, suppose the alphabet is (a, e, i, O, u, !), and a fixed model is used
with probabilities shown

\begin{table}[]
	\setlength{\extrarowheight}{0.2cm}
	\begin{tabular}{|l|l|l|}
		\hline
		Symbol & Probability & Range        \\ \hline
		a      & 0.2         & {[}0, 0.2)   \\ \hline
		e      & 0.3         & {[}0.2, 0.5) \\ \hline
		i      & 0.2         & {[}0.5, 0.7) \\ \hline
		o      & 0.1         & {[}0.7, 0.8) \\ \hline
		u      & 0.1         & {[}0.8, 0.9) \\ \hline
		!      & 0.1         & {[}0.9, 1.0) \\ \hline
	\end{tabular}
\end{table}

We have to transmit the message 'eaii!'. Initially, both encoder and decoder know that the range is [0, 1). After seeing the first symbol, e, the encoder narrows it to [0.2, 0.5), the range the model allocates to this symbol. The second symbol, a, will narrow this new range to the first one-fifth of it, since a has been allocated [0, 0.2). This produces [O.2, 0.26), since the previous range was 0.3 units long and one-fifth of that is 0.06. The next symbol, i, is allocated [0.7, 0.8),which when applied to [0.2, 0.26) gives the smaller range [0.242, 0.248). Proceeding in this way, the en-coded message builds up as follows:

Initially [0, 1)

After seeing

e [0.2, 0.5)
\\
a [0.2, 0.26)
\\
i [0.242, 0.248)
\\
i [0.2462, 0.2468)
\\
! [0.24674, 0.2468) \\

Suppose all the decoder knows about the message is the final range, [0.24674, 0.2468) .It can -immediately deduce that the first character was e since the range lies entirely within the space the model of Table allocates for e. Now it can simulate the operation of the encoder:

Initially [0, 1)
\\
After seeing e [0.2, 0.5)
\\

This makes it clear that the second character is a,since this will produce the range

After seeing a [0.2, 0.26),which entirely encloses the given range [0.24674, 0.2468). Proceeding like this, the decoder can identify the whole message. However, the decoder will face the problem of detecting the end of the message, to determine when to stop decoding. After all, the single number 0.0 could represent any of a, aa, aaa, aaaa, . . .  . To resolve the ambiguity, we ensure that each message ends with a special EOF symbol known to both encoder and decoder. For the alphabet of Table I, "!" will be used to terminate messages  When the decoder sees this symbol,it stops decoding.

Relative to the fixed model of Table, the entropy
of the five-symbol message ‘eaii!’ is

$$-\log{0.3} - \log{0.2} - \log{0.1} - \log{0.1} - \log{0.1} = -\log{0.00006} =4.22$$

@@

In computing, Deflate may be a lossless data compression file format that uses both  LZ77 and Huffman coding. It was designed by Phil Katz, for version 2 of his PKZIP archiving tool. Deflate was later specified in RFC 1951 \cite{deflate}
The deflate compressor is given an excellent deal of flexibility to compress the info . The programmer must design smart algorithms to form the proper choices, but the compressor does have choices about the way to compress data.

There are three modes of compression that the compressor has available:

\begin{enumerate}
	\item Not compressed at all. This is an intelligent choice for, say, data that's already been compressed. Data stored during this mode will expand slightly, but not as much as it would if it was already compressed and any other compression methods was tried upon it.

	\item Compression, first with LZ77 then with Huffman coding. The trees used to compress during this mode are defined by the Deflate specification itself and no extra space must be taken to store those trees.

	\item Compression, first with LZ77 then with Huffman coding with trees that the compressor creates and stores along side the data .
	The data is choppy in ``blocks,'' and every block uses a single mode of compression. If the compressor wants to change  from non-compressed storage to compression with the trees defined by the specification, or to compression with specified Huffman trees, or to compression with a different pair of Huffman trees, the present block must be ended and another one begun.

\end{enumerate}

\vspace{0.6in}

@@

\subsection{Related Work}
Data compression has recently been used for data mining. Benedetto et al. used gzip for language recognition, authorship attribution, and language classification \cite{benedetto2002language}. Cilibrasi and Vit´anyi presented a method for clustering by compression, which is based on the normalized compression distance
(NCD) \cite{li2004similarity}, and reported the evidence of successful application in areas as diverse as genomics, virology, music, astronomy, etc \cite{cilibrasi2005clustering}. Bratko et al. investigated an approach to
spam filtering based on statistical data compression models, and their empirical evaluations indicated that their approach outperforms currently established spam filters based on machine learning algorithms \cite{bratko2006spam}. Marton et al. reported the effectiveness and behavior of different compression-based text classification methods on English text \cite{marton2005compression}.

On the other hand, machine learning approaches have been frequently applied to Twitter mining. Irani et al. devised machine learning methods such as the decision tree for identifying the tweets in which spammers misused
trending topics by using tweet text and the associated web
pages with the tweet \cite{irani2010study}. Sriram et al. devised a Naive Bayes
classifier for identifying tweet types such as news, events, opinions, deals, and private messages based on the author information and tweet texts \cite{sriram2010short}. Sakaki et al. devised a support vector machine for finding tweets related to an event (e.g., earthquake) \cite{sakaki2010earthquake}. To their knowledge, there was no application of data compression to Twitter mining.

@@

This paper reports a rather different viewpoint on the whole compression domain. The energy required to send a bit via wireless transmission is close to 1000 times higher than the energy required for a regular 32 bit operation on a computer \cite{note1998writing}. The article reports the fact that compressing and decompressing information before and after transmission is more energy expensive compared to the case without any compression. The paper suggests solutions to this problem and they are able to achive an energy reduction of close to 51\%.

\subsection{Lossless Data Compression of low-bandwidth devices}
Compression algorithms are versatile. They can be applied at a lot of points in the hardware-software spectrum. When compression is applied in hardware, the benefits and costs propagate to all aspects of the system. Compression in software may
have a more dramatic effect, but for better or worse, its effects will be less global. An all-purpose header compression scheme (not confined to TCP/IP or any particular protocol) appears in \cite{lilley2000unified}. TCP/IP payloads can be compressed as well with IPComp \cite{shacham2001rfc3173}, but this can be wasted effort if data has already been compressed at the application layer.

LBFS or Low Bandwidth File System leverages the similiarities between the data stored on the client and the server, and only exchanges data blocks that differ \cite{muthitacharoen2001low}. Compression is applied before the data is transmitted. Rsync \cite{tridgell2000efficient} is a protocol for efficient file transfer which preceded LBFS. A protocol-independent scheme for text compression,
NCTCSys, is presented in \cite{motgi2001network}

Along with remote proxy servers which may cache or
reformat data for mobile clients, splitting the proxy between client and server has been proposed to implement certain types of network traffic reduction for HTTP transactions \cite{housel1996webexpress} \cite{krashinsky2003efficient}. Because the delay required for manipulating data can be small in comparison with the latency
of the wireless link, bandwidth can be saved with little
effect on user experience. Alternatively, compression
can be built into servers and clients as in the mod gzip
module available for the Apache webserver and HTTP
1.1 compliant browsers \cite{hyperspace}. Delta encoding, the transmission of only parts of documents which differ between
client and server, can also be used to compress network
traffic \cite{hunt1996empirical} \cite{mogul1999trace} \cite{mogul1997potential} \cite{santos1998increasing}

\subsection{Methodologies and Summary}
The tests were done on a Compaq Personal Server codenamed "Skiff".\cite{compaq}

The energy required for compression and decompression are almost directly proportional to time required for executing. The energy required is observed to be more for aggressively compressed data due to the large number of memory references. Even though the energy requirement is proportional to the execution time, using the fastest algorithm for compression and decompression doesn't reduce the energy footprint. They were able to conclude the fact that reducing energy is not as simple as picking the fastest compression algorithm. To facilitate such dynamic energy adjustment, they were working on EProf: a portable, realtime, energy profiler which plugs into the PC-Card socket of a portable device \cite{koskelin2002eprof}

@@

\section{On the Compressive Power of Boolean Threshold Autoencoders \cite{melkman2020compressive}}

An autoencoder is a layered neural network whose structure can be viewed as consisting of an encoder, which compresses an input vector of dimension D to a vector of low dimension d, and a decoder which transforms the low-dimensional vector back to the original input vector (or one that is very similar). In this paper they explore the compressive power of autoencoders that are Boolean threshold networks by studying the numbers of nodes and layers that are required to ensure that each vector in a given set of distinct input binary vectors is transformed back to its original\cite{ackley1985learning}. It is shown that that for any set of n distinct vectors there exists a seven-layer autoencoder with the smallest possible middle layer, (i.e., its size is logarithmic in n), but that there is a set of n vectors for which there is no three-layer autoencoder with a middle layer of the same size. In addition we present a kind of trade-off: if a considerably larger middle layer is permissible then a five-layer autoencoder does exist. The results obtained suggest that it is the decoding that constitutes the bottleneck of autoencoding. For example, there always is a three-layer Boolean threshold encoder that compresses n vectors into a dimension that is reduced to twice the logarithm of n.\cite{anderson1988neurocomputing} \cite{kingma2013auto} \cite{doersch2016tutorial}

@@

@@

When large groups of similar files are stored, such as a group of sequential videos, they can be combined into archive files. Archive files don't have to be compressed, but they are often several gigabytes in size, so they are usually compressed to save storage space and transmission time. Most compression programs also have the ability to archive files into one large file. Most operating systems will compress their backup files, which are very large archive files, since these files just take up space until the need for them arises.

@@
